I would especially like to thank my advisor and friend, Mykel Kochenderfer, for his continued guidance over the past decade.
Our time together at MIT Lincoln Laboratory has certainly shaped me into the researcher am I today.
The positivity in Mykel's leadership is inspirational and his high level of integrity and honesty encouraged me to always do my best.
He is a model leader and I thank him for the incredible opportunity both at MIT Lincoln Laboratory at here at Stanford.
I'd also like to thank Professor Dorsa Sadigh for being my secondary research adviser and for her advice regarding this thesis.

As with many theses, I am standing on the shoulders of giants.
I would like to thank Ritchie Lee from NASA Ames for his original development of the adaptive stress testing approach and for his patience and guidance as he helped shape my own ideas.
I want to thank Anthony Corso, Mark Koren, and Alex Koufos for always listening to my ideas, encouraging my excitement in the AI safety field, and always providing constructive feedback. Without their advice, this work would not have been possible.
I'd also like to thank members of the Stanford Intelligent Systems Laboratory (SISL) for their encouragement and willingness to listen; particularly Bernard Lange, Shushman Choudhury, Jayesh Gupta, Sydney Katz, and Tomer Arnon.
Because this work is built off of other open-source software, I'm forever indebted to the SISL members that developed the POMDPs.jl ecosystem and other open-source tools; this includes Zachary Sunberg, Maxim Egorov, Tim Wheeler, and Xiaobai Ma.
I also acknowledge Shreyas Kowshik for his initial implementation of the TRPO and PPO algorithms in Julia.
I want to extend a thank you to Edward Balaban at NASA Ames for the opportunity to work on a decision making under uncertainty system in a high-profile NASA mission.

I have also had the pleasure to work with James G. O'Brien as an undergraduate researcher while at Wentworth and I'm grateful for his inspiration and trust he provided me. I owe an enormous debt to everyone I have interacted with while at MIT Lincoln Laboratory over the years---they each played a role in shaping me into a better scientist, engineer, analyst, and friend. This includes Ted Londner, Michael Owen, Wes Olson, Ian Jessen, Adam Panken, Tomas Elder, Cindy McLain, Luis Alvarez, Tan Trinh, Robert Klaus, Justin MacKay, Jared Wikle, Emilie Cowen, Tom Teller, Adam Gjersvik, Sam Wu, Anshu Das, Jack Lepird, Charles Leeper, and Dan Griffith. Particular appreciation goes to Jeff Bezanson for Julia and showing me its divinity. Also a special thanks to Neal Suchy from the Federal Aviation Administration for his admiration and his faith in my work.

Part of this work had the support from GE's Global Research Center and GE Aviation through the Stanford Center for AI Safety.
I want to thank each of these organizations for their fascinating challenges and allowing me to explore research ideas that fit not only my interests but had large industrial impacts.
I also want to thank the NASA AOSP System-Wide Safety Project for partially supporting this work and Jerry Lopez, Nicholas Visser, and Joachim Hochwarth for their engineering guidance.

My family and friends have always been there for me, even as we are physically distant.
My Mom, Dad, and siblings---Travis, Emily, and Jake---are a big reason I have core values that have helped me succeed.
Their love and support is infinite and I could not thank them enough for the life they've provided me.
My wife's family have also been incredibly supportive and I am thankful for their immense encouragement.
To everyone back in Rockport, MA and beyond, you've seen me grow through every phase in my life, and that bond is irreplaceable; so thank you.

Lastly, but most importantly, I want to thank my wife, Eva Moss, for always being supportive and growing with me during my graduate studies.
Eva, you always make me laugh, smile, and think deeply, which has shaped me into a better person because of it.
Your logical thinking helps me check my opinions at the door.
Your flexibility in leaving our home back in Massachusetts and moving out to California tremendously helped in reducing the stress of graduate school---I love you and I am forever grateful.
